### 2015-04-03 Workshop2015/toSubmit/introduction.tex
Version by Nadia et Chirine

\color{black}
The advent of cloud computing imposed a new model for resource consuming that is not concerned
 with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially unlimited resources. Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques have to be revisited considering weakly curated and modeled data sets. This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. Therefore, we believe in the benefits of SLA-based data integration as an approach for better meeting  user requirements.
\color{red}
In order to do so, several granularities of SLA must be considered: (i) at the cloud level: the SLA ensured by providers regarding data; (ii) at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally (iii) at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).

\color{black}
%To better understand our problem, let us consider an example from the domain of energy
%management. We assume we are interested in queries like: \textit{Give a list of energy providers that can provision 1000 KW-h, in the next 10 seconds, that are close to my city, with a cost of 0,50 Euro/KW-h and that are labelled as green?} \\
% The user demanded to apply a special encryption algorithm to sensitive data if data has to be transferred between providers or between physical sites during the integration process (Constraint1). Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2). We consider a simplified SLA cloud contract inspired in the cheapest contract provided by Azure: \textit{cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  1~GB of storage.} 
%The user is ready to pay a maximum of \textit{\$5 as total query cost}; she requests that only  \textit{green} energy providers should be  listed (provenance), with at least  \textit{85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least 90$\%$ and a response time of  \textit{0,01 s}. She demands to contact only data providers with a threshold of trust .

@@

 \color{red}
Accordingly, the remainder of this paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes. Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by conciliating SLA's provided by services and user's profiles expressing QoS preferences. Profiles specify preferences about the data they want to consume and the conditions in which they must be processed and delivered. 
%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
Finally \ref{sec:conclusions} concludes the papers and discusses future work.

\color{black}

>>>>

\color{black}
The advent of cloud computing imposed a new model for resource consuming that is not concerned
 with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially unlimited resources. Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques have to be revisited considering weakly curated and modeled data sets. This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. Therefore, we believe in the benefits of SLA-based data integration as an approach for better meeting  user requirements.

To do so, several granularities of SLA must be considered: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).

%To better understand our problem, let us consider an example from the domain of energy
%management. We assume we are interested in queries like: \textit{Give a list of energy providers that can provision 1000 KW-h, in the next 10 seconds, that are close to my city, with a cost of 0,50 Euro/KW-h and that are labelled as green?} \\
% The user demanded to apply a special encryption algorithm to sensitive data if data has to be transferred between providers or between physical sites during the integration process (Constraint1). Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2). We consider a simplified SLA cloud contract inspired in the cheapest contract provided by Azure: \textit{cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  1~GB of storage.} 
%The user is ready to pay a maximum of \textit{\$5 as total query cost}; she requests that only  \textit{green} energy providers should be  listed (provenance), with at least  \textit{85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least 90$\%$ and a response time of  \textit{0,01 s}. She demands to contact only data providers with a threshold of trust .

@@

Accordingly, the remainder of this paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments. Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process. Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.  Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach.
